An Introduction to the taxize package

### 2012-10-14 inst/doc/taxize-intro.Rnw
hmm, need to set API-keys...

\section{Tropicos}
<<>>=
head(tp_getacceptednames(id = 25503923))
head(tp_getsynonyms(id = 25509881))
@

\section{uBio}
\subsection{Search uBio using the namebank\_search API method}
<<>>=
ubio_namebank(searchName = 'elephant', sci = 1, vern = 0)
head( ubio_namebank(searchName = 'Helianthus annuus', sci = 1, vern = 0)[,-c(2,3)] )
out <- lapply(list('Helianthus debilis','Astragalus aduncus'), function(x) ubio_namebank(searchName = x, sci = 1, vern = 0))
head( out[[2]][,-c(2,3)] ) # just Astragalus aduncus output
@

>>>>

\section{Tropicos}
<<>>=
# need key
#head(tp_getacceptednames(id = 25503923))
#head(tp_getsynonyms(id = 25509881))
@

\section{uBio}
\subsection{Search uBio using the namebank\_search API method}
<<>>=
# need key
# ubio_namebank(searchName = 'elephant', sci = 1, vern = 0)
# head( ubio_namebank(searchName = 'Helianthus annuus', sci = 1, vern = 0)[,-c(2,3)] )
# out <- lapply(list('Helianthus debilis','Astragalus aduncus'), function(x) ubio_namebank(searchName = x, sci = 1, vern = 0))
# head( out[[2]][,-c(2,3)] ) # just Astragalus aduncus output
@
